---
title: "RNA Velocity"
author: "Trevor Enright"
date: "9/16/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: true
params:
  inputobs: "PATH/TO/OBS.tsv"
  seurat: "seurat_path"
  genes: "string of genes"
  contrast: "Condition"
  cluster: "predicted.id"
  wave: "current wave"
  out_dir: "/path/to/out"
  contrast_name: "contrast"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(Seurat)
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)
library(gridExtra)
library(xtable)
library(tidyr)
library(rlang)
#library(limma)
library(plotly)
library(ggrepel)
library(ggpubr)
library(knitr)
library(DT)

contrast <- params$contrast

scvelo_path <- params$inputobs
seurat <- params$seurat
genes <- params$genes
seurat_cluster <- params$cluster
outdir = dirname(paste(getwd(),params$out_dir,sep="/"))
wave = params$wave
contrast_name = params$contrast_name

######################################### Custom Color
Color_hex = c("#67CAD4","#B0207E") #purple for FPD, teal for HD
Order_plot = c("HD","FPD")
names(Color_hex) = Order_plot

#####################################
```

```{r echo = F, message = F, warning= F}
#functions:

VlnPlot_stats <- function(seuratObj, group_by, gene_signature, color = NULL){
  
  comparisons <- unique(seuratObj@meta.data[group_by][,1])
  comp_list <- list()
  for (i in 1:length(comparisons)){

	  for(j in (i+1):length(comparisons)){

		if (j > length(comparisons)){
		 
		  break
		}
		
		comp_list[[paste(i,j,sep="_")]] <- c(comparisons[i],comparisons[j])

		}
	}
  
  plot_case1 <- function(signature, y_max = NULL, comparisions = comparisons){
    
    VlnPlot(seuratObj, features = signature,
            pt.size = 0, 
            group.by = group_by, 
            y.max = y_max, # add the y-axis maximum value - otherwise p-value hidden
            cols = color
    ) + stat_compare_means(comparisons = comp_list, label = "p.value", method = "t.test")  
  }
  plot_list <- list()
  for (gene in gene_signature) {
    max_try <- try(max(FetchData(seuratObj, vars = gene)))
    if(class(max_try) == "try-error"){
      next
    } else {
      plot_list[[gene]] <- plot_case1(signature = gene, y_max = max_try + 3)
    }
  }
  cowplot::plot_grid(plotlist = plot_list)
  #file_name <- paste0(file_name, "_r.png")
  #ggsave(file_name, width = 14, height = 8*())
}

```

# RNA velocity 

RNA velocity leverages unspliced pre-mRNAs and mature, spliced mRNAs can be distinguished in common single-cell RNA-seq protocols, the former detectable by the presence of introns.   For each gene, a steady-state-ratio of pre-mature (unspliced) and mature (spliced) mRNA counts is fitted, which constitutes a constant transcriptional state. Velocities are then obtained as residuals from this ratio. Velocities are vectors in gene expression space and represent the direction and speed of movement of the individual cells.

```{r echo = F, eval = T}

scvelo <- read.delim(paste(getwd(),scvelo_path,sep="/"))

string_to_list <- function (x) {
  return(unlist(strsplit(gsub("\\s", ",", x) ,",")))
}

genes_of_interest <- string_to_list(genes)

unique_clusters <- unique(scvelo$cluster)

```

# Spliced vs Unspliced by Sample

```{r echo = F, eval = T, out.width='100%'}
par(mfrow=c(1,1))

get_percentage <- function(df,groupby){
  #input: 
    #df     -> dataframe from scvelo (scv.obs)
    #groupby -> choose what column to subset the percentages by
  #returns ggplot  percent spliced and unspliced
  
  #make df into long format
  df <- reshape(df, direction = "long", varying = list(c("initial_size_spliced","initial_size_unspliced")), v.names = "intial_size", timevar = "splice_status", times = c("initial_size_spliced","initial_size_unspliced")) 

  
 #change the names for readability
df$splice_status <- gsub("initial_size_unspliced","unspliced",gsub("initial_size_spliced","spliced",df$splice_status))

#combine group names with splice_status to make a place holder for actual percentages
df$group_percent <- paste(df[[groupby]],df$splice_status,sep="_")

#get max height for each group
# get the percentage for each group
  DF_list <- list()
  Max_H <- 0
  for(group in unique(df[[groupby]])){
    cur_set <- df[which(df[[groupby]] == group),]
    Max_H <- max(Max_H,sum(cur_set[which(cur_set$splice_status == "spliced"),"initial_size"]))
    spliced <- sum(cur_set[which(cur_set$splice_status == "spliced"),"intial_size"])/sum(cur_set$intial_size)
    DF_list[[group]] <- spliced
  }
  
#go through place holder and substitute percentages
  new_prop <- df$group_percent
  for (cell in unique(df$group_percent)){
    n_len <- length(unlist(strsplit(cell,"_")))
    group <- paste(unlist(strsplit(cell,"_"))[1:(n_len-1)],collapse = "_")
    status <- unlist(strsplit(cell,"_"))[n_len]
    spliced_prop <- round(DF_list[[group]]*100,1)
    unspliced_prop <- round((1-DF_list[[group]])*100,1)
    new_prop <- gsub(paste(group,"spliced",sep="_"),paste0(spliced_prop,"%"),gsub(paste(group,"unspliced",sep="_"),paste0(unspliced_prop,"%"),new_prop))
  }
  Max_H <- Max_H + (0.1*Max_H)
  df$GP <- new_prop
  df$GroupBY <- df[[groupby]]
  ggplot(df, aes(x = splice_status, y = intial_size, fill = splice_status )) + geom_bar(stat = "identity")  + facet_wrap(~GroupBY) + theme(axis.text.x = element_text(angle = 50, vjust = 0.5, hjust=1)) + ylab("counts") + geom_text(aes(x=splice_status,y=Max_H,label = GP))
  
}
get_percentage(scvelo, groupby = "samples")
```


# Velocity UMAPS


## No batch correction  {.tabset .tabset-fade .tabset-pills}


### Stream

```{r  ,eval = T, echo = F, message = F, warning = F, out.width='100%'}
base_path <- paste(outdir,"figures",sep="/")

file_path <- paste(base_path,"scvelo_scvelo_stream.png",sep="/")
if(file.exists(file_path)){   knitr::include_graphics(path = file_path) } 

```

### Confidence  


* The speed or rate of differentiation is given by the length of the velocity vector.
* The coherence of the vector field (i.e., how a velocity vector correlates with its neighboring velocities) provides a measure of confidence.

```{r  ,eval = T, echo = F, message = F, warning = F, out.width='100%'}

file_path <- paste(base_path,"scvelo_scatter_confidence.png",sep="/")
if(file.exists(file_path)){   knitr::include_graphics(path = file_path) } 
```

```{r  ,eval = T, echo = F, message = F, warning = F, out.width='100%'}

file_path <- paste(base_path,"scvelo_scvelo_stream.png",sep="/")
if(file.exists(file_path)){   knitr::include_graphics(path = file_path) } 
```


## Batch balanced KNN (using samples as batches)  {.tabset .tabset-fade .tabset-pills}

```{r  ,eval = T, echo = F, message = F, warning = F, out.width='100%'}

file_path <- paste(base_path,"scvelo_scvelo_stream_batch.png",sep="/")
if(file.exists(file_path)){   knitr::include_graphics(path = file_path) } 
```

Batch balanced kNN alters the kNN procedure to identify each cell’s top neighbours in each batch separately instead of the entire cell pool with no accounting for batch. Aligns batches in a quick and lightweight manner. https://scanpy.readthedocs.io/en/stable/external/scanpy.external.pp.bbknn.html https://academic.oup.com/bioinformatics/article/36/3/964/5545955

# Individual samples {.tabset .tabset-fade .tabset-pills}


```{r echo = F, eval = T}

paths <- read.delim(sprintf("../input/%s_locations.tsv",wave))
working_names <- basename(as.vector(paths[,1]))


#names(working_names) <- working_code_names
#common_name <- unname(working_names[working_samples])

base_path = paste(getwd(),"../results/ind",sep = "/")

```

```{r, results = "asis",echo=F}

for (i in 1:length(working_names)){
  cur_sample <- working_names[i]
  cur_path <- paste(base_path,cur_sample,"figures",sep="/")
  file_path <- paste(cur_path,"proportions.png",sep="/")
  if(file.exists(file_path)){
    cat("## ",cur_sample,"\n\n")
    cat('\n![Proportions](',file_path,')\n')
    cat('\n')
  }
  file_path <- paste(cur_path,"scvelo_scatter_confidence.png",sep="/")
  if(file.exists(file_path)){
    cat('\n![Scatter confidence](',file_path,')\n')
    cat('\n')
  }
  file_path <- paste(cur_path,"scvelo_scvelo_stream.png",sep="/")
  if(file.exists(file_path)){
    cat('\n![Stream](',file_path,')\n')
    cat('\n')
  }
}
```

# Phase Portrait and Violins

Transcriptional induction for a particular gene results in an increase of (newly transcribed) precursor unspliced mRNAs while, conversely, repression or absence of transcription results in a decrease of unspliced mRNAs. Spliced mRNAs is produced from unspliced mRNA and follows the same trend with a time lag. Time is a hidden/latent variable. Thus, the dynamics needs to be inferred from what is actually measured: spliced and unspliced mRNAs as displayed in the phase portrait.

[Animation](https://user-images.githubusercontent.com/31883718/80227452-eb822480-864d-11ea-9399-56886c5e2785.gif)

```{r echo=F,warning=F,message=F,error = F, include = F}

run2process <- read.delim(sprintf("../input/%s_locations.tsv",wave), header = T)

sample_cells <- c()
seuratObj <- readRDS(seurat)
for (i in 1:dim(run2process)[1]){
		sample_cells <- c(sample_cells,names(which(sapply(Cells(seuratObj),function(x) { unlist(strsplit(x,"_"))[2]}) == as.character(run2process[i,2]))))
}
#for (i in list_int){
#		sample_cells <- c(sample_cells,names(which(sapply(Cells(seuratObj),function(x) { unlist(strsplit(x,"_"))[2]}) == as.character(i))))
#}

seuratObj <- subset(seuratObj, cells = sample_cells)

GOI <- list()
DefaultAssay(seuratObj) <- "RNA"

#seuratObj[[contrast]] <- factor(x = seuratObj[[contrast]][,1],levels = Order_plot)
base_path <- paste(outdir,"Analyze","figures",sep="/")

for (clust in unique_clusters){
	grep_it <- sprintf("scatter_phase_%s",gsub("/",".",clust))
	genes_in_file <- unname(sapply(grep(grep_it,list.files(base_path),value = T), function(x){ unlist(strsplit(x,"_"))[5]}))
	genes_in_files <- gsub(".png","",genes_in_file)
	keep_cells <- rownames(seuratObj[[seurat_cluster]])[which(seuratObj[[seurat_cluster]] == clust)]
	sub_seurat <- subset(seuratObj, cells = keep_cells)
	top_velocity <- try(read.delim(sprintf("%s/../top_%s_velocity_genes.tsv",base_path,gsub("/",".",clust))))
	if(class(top_velocity) != "try-error"){
		GOI[[as.character(clust)]] <- sort(unique(c(genes_of_interest, genes_in_files, as.character(head(top_velocity[,2],n=10)),as.character(head(top_velocity[,3],n=10)),as.character(tail(top_velocity[,2],n=10)),as.character(tail(top_velocity[,3],n=10)))))
	} else {
		GOI[[as.character(clust)]] <- sort(unique(c(genes_of_interest, genes_in_files)))
	}
	#genes_of_interest <- unique(c(genes_of_interest,top_velocity[nrow(top_velocity)-10:nrow(top_velocity),2],top_velocity[1:10,2]))
	for (gene in GOI[[as.character(clust)]]){
		file_path <- paste(base_path,sprintf("VlnPlot_%s_%s_exp.png",gsub("/",".",clust),gene),sep="/")
		if(!(file.exists(file_path))){
			p_plot <- try(pplot <- VlnPlot_stats(sub_seurat, group_by = contrast, gene_signature = gene, color = Color_hex))
			if(class(p_plot) != "try-error"){
				ggsave(basename(file_path), plot = p_plot, path = dirname(file_path), device = "png")
			}
		}
		file_path <- paste(base_path,sprintf("FeaturePlot_%s_%s_exp.png",gsub("/",".",clust),gene),sep="/")
		if(!(file.exists(file_path))){
			p_plot <- try(pplot <- FeaturePlot(sub_seurat, features = gene, split.by = contrast))
			if(class(p_plot) != "try-error"){
				ggsave(basename(file_path), plot = p_plot, path = dirname(file_path), device = "png")
			}
		}
	}
	#df_complete <- paste(base_path,"..",sprintf("anova_%s_mean_velocity_merged_DE.tsv",gsub("/",".",clust)),sep="/")
	DE_path <- paste(base_path,"..",sprintf("FindMarkers_%s_by_%s_RNA_DE.tsv",gsub("/",".",clust),contrast),sep="/")
	if(!(file.exists(DE_path))){
		#file_path <- paste(base_path,"..",sprintf("anova_%s_mean_velocity_genes.tsv",gsub("/",".",clust)),sep="/")
		#df <- read.delim(file_path)
		#df <- df[,-1]
		#df$label <- paste(df$gene," : ", colnames(df)[1], " : ",df[,1],", " , colnames(df)[2]," : ", df[,2], sep="")
		
		Idents(sub_seurat) <- contrast
		DE <- FindMarkers(sub_seurat, ident.1 = contrast_name)
		colnames(DE) <- c("p_val_DE", colnames(DE)[2:length(colnames(DE))])
		DE$gene = rownames(DE)
		write.table(DE,file = DE_path,sep="\t",quote=F,col.names = T,row.names = T)
		#merged_df <- merge(DE,df, by = "gene")
		#write.table(merged_df,file = df_complete,sep="\t",quote=F,col.names = T,row.names = T)
	}
	
	
}

#v2 = c('3','4','5','6','30','1','2','11','12','13','14','9','10','7','8')
#v3 = c('15','16','17','18','19','20','21','26','22','27','23','24','25','29','28','31')
#unenriched <- c(3,4,5,6,1,16,19,30,20,26,22,24,29,28,31)
#all_n <- c(v2,v3)
#enriched <- which(!(sort(as.numeric(all_n)) %in% sort(as.numeric(unenriched))))
#enriched_cells <- c()
#for (i in enriched){enriched_cells <- c(enriched_cells,names(which(sapply(Cells(seuratObj),function(x) { unlist(strsplit(x,"_"))[2]}) == i)))} 
#unenriched_cells <- c()
#for (i in unenriched){unenriched_cells <- c(unenriched_cells,names(which(sapply(Cells(seuratObj),function(x) { unlist(strsplit(x,"_"))[2]}) == i)))} 
#enrichment_type <- c(rep("enriched",length(enriched_cells)),rep("unenriched",length(unenriched_cells)))
#
#> names(enrichment_type) <- c(enriched_cells,unenriched_cells)
#seuratObj <- AddMetaData(seuratObj, enrichment_type, col.name = "enrichment")
#> v2_cells <- c()
#> for (i in v2) {v2_cells <- c(v2_cells,names(which(sapply(Cells(seuratObj),function(x) { unlist(strsplit(x,"_"))[2]}) == i)))} 
#kit_type <- c(rep("v2",length(v2_cells)),rep("v3",length(v3_cells)))
#> kit_type <- c(rep("v2",length(v2_cells)),rep("v3",length(v3_cells)))
#> names(kit_type) <- c(v2_cells,v3_cells)
#> seuratObj <- AddMetaData(seuratObj, kit_type, col.name = "kit")
#Idents(seuratObj) <- "kit"
#subset_seurat <- subset(seuratObj, subset = enrichment == "unenriched")
#DefaultAssay(subset_seurat) <- "RNA"
#df <- FindAllMarkers(seuratObj, features=velocity_kit$genes, test.use = "t")
#df_velocity <- merge(velocity_kit,df, by.x = "genes", by.y = "gene")      
#df_velocity <- subset(df_velocity, subset = cluster == "v2") 
#df_velocity <- df_velocity[,-2]
#write.table(df_velocity,sep ="\t", quote = F, header = T)
#


```


## Cell Types {.tabset .tabset-fade .tabset-pills}

```{r echo = F, results='asis'}
base_path <- paste(outdir,"figures",sep="/")

for (clust in unique_clusters){
	scvelo_sub <- subset(scvelo, cluster == clust)
	cat("\n### ",clust," {.tabset .tabset-fade .tabset-pills}\n")
	file_path <- paste(base_path,"..","Analyze/figures",sprintf("stats_velocity_length_%s.png",gsub("/",".",clust)),sep="/")
		if(file.exists(file_path)){
			cat('\n![By Condition](',file_path,')\n\n')
		}
	
		
	file_path <- paste(base_path,"..","Analyze/figures",sprintf("violinorig_velocity_length_%s.png",gsub("/",".",clust)),sep="/")	
	if(file.exists(file_path)){
			cat('\n![By Sample](',file_path,')\n\n')
		}
	
	
	DE_path <- paste(base_path,"../Analyze",sprintf("FindMarkers_%s_by_%s_RNA_DE.tsv",gsub("/",".",clust),contrast),sep="/")
	DE_markers <- read.delim(DE_path)
	velocity_path <- paste(base_path,"../Analyze",sprintf("wilcoxon_%s_velocity.tsv",gsub("/",".",clust)),sep="/")
	velocity_markers <- read.delim(velocity_path)
	
	
	df <- merge(DE_markers,velocity_markers,by.x = "gene",by.y = "names", all = F)
	df <- df[,-which(colnames(df) == "X")]
	df_na <- df[-which(is.na(df$logfoldchanges)),]
	cutoff <- min(abs(quantile(df_na$logfoldchanges)[2]),abs(quantile(df_na$logfoldchanges)[4]))*1.5
	ix_label <- which( df_na$logfoldchanges > cutoff |  df_na$logfoldchanges < -cutoff)
	df_na["label"] <- ""
	df_na$label[ix_label] <- df_na$gene[ix_label]
	p_plot <- ggplot(df_na, aes(x = logfoldchanges, y = -log10(pvals_adj) ,label = label)) + geom_point(color = ifelse(df_na$label == "", "grey50", "red")) +  geom_text_repel() + xlab(sprintf("log2 fold change RNA velocity (wilcoxon rank test), label: %s",round(cutoff,2))) + ylab("-log10 adjusted p-value RNA velocity (wilcoxon rank test)")
	
	#print(p_plot)
	
	cutoff <- min(abs(quantile(df_na$avg_logFC)[2]),abs(quantile(df_na$avg_logFC)[4]))*1.5
	ix_label <- which( df_na$avg_logFC > cutoff |  df_na$avg_logFC < -cutoff)
	df_na["label"] <- ""
	df_na$label[ix_label] <- df_na$gene[ix_label]

	#p_plot <- ggplot(df_na, aes(x = avg_logFC, y = -log10(p_val_adj) ,label = label)) + geom_point(color = ifelse(df_na$label == "", "grey50", "red")) +  geom_text_repel() + xlab(sprintf("log2 fold change RNA expression (wilcoxon rank test), label: %s",round(cutoff,2))) + ylab("-log10 adjusted p-value RNA expression (wilcoxon rank test)")
	
	
	#p_plot <- ggplot(df, aes(x = -log(p_val_DE), y = -log(pvals),label = gene)) + geom_point() +  geom_text_repel() + xlab("-log(p_val) RNA (wilcoxon rank test)") + ylab("-log(p_val) velocity (wilcoxon rank test)")

	#print(p_plot)
	velocity_anova <- paste(base_path,"../Analyze",sprintf("anova_%s_mean_velocity_genes.tsv",gsub("/",".",clust)),sep="/")
	velocity_anova <- read.delim(velocity_anova)
	velocity_anova <- velocity_anova[,c(2,3,4)]
	df_all <- merge(df_na,velocity_anova, by = "gene")
	df_all2 <- gather(df_all,"condition","velocity_mean",FPD,HD)
	p_plot <- ggplot(df_all2, aes(x = condition, y = velocity_mean )) + geom_violin( aes(fill= condition)) + scale_fill_manual(values=Color_hex) + stat_compare_means(comparisons = list(names(Color_hex)), label = "p.value", method = "t.test") + geom_boxplot(width=0.1, color="black", alpha=0.2)
	print(p_plot)
	
	
	
	cat("p_val_DE,avg_logFC,pct.1,pct.2,p_val_adj : RNA expression test: wilcoxon rank sum between FPD and HD \n")
	cat("scores,pvals,pvals_adjusted,logfoldchanges : RNA velocity test: wilcoxon rank sum between FPD and HD \n")
	cat("FPD and HD: means of velocity score\n")
	#df <- df[-which(is.na(df$logfoldchanges)),]
	print(kable(df_all[,!(names(df_all) == "label")]))
	write.table(df_all[,!(names(df_all) == "label")],paste(base_path,"../Analyze",sprintf("velocity_%s_DE.tsv",gsub("/",".",clust)),sep="/"), quote=F,col.names = T,row.names = T)
	file_path <- paste(base_path,sprintf("bar_plot_%s_clust.png",gsub("/",".",clust)),sep="/")
	if(!(file.exists(file_path))){
		cur_prop <- subset(scvelo, cluster == clust)
		
		p_plot <- try(get_percentage(cur_prop, groupby = "samples"))
		if(class(p_plot) != "try-error"){
			ggsave(basename(file_path), plot = p_plot, path = dirname(file_path), device = "png")
		}
	}
	if(file.exists(file_path)){
		cat('\n![Bar Plot](',file_path,')\n\n')
	}
	
	
	
	genes_of_interest <- GOI[[as.character(clust)]]
	for (i in 1:length(genes_of_interest)){
		cur_gene <- genes_of_interest[i]
		
		file_path <- paste(base_path,"..","Analyze/figures",sprintf("scvelo_scatter_gene_cluster_%s_%s.png",gsub("/",".",clust),cur_gene),sep="/")
		if(file.exists(file_path)){
			cat("\n\n#### ",cur_gene,"\n\n")
			cat('\n![Scatter](',file_path,')\n\n')
		}
		
		file_path <- paste(base_path,"..","Analyze/figures",sprintf("scvelo_scatter_phase_%s_%s.png",gsub("/",".",clust),cur_gene),sep="/")
		if(file.exists(file_path)){
			cat('\n![Phase](',file_path,')\n\n')
			cat('G1 = red, G2M = blue, S = green')
		}	
		
		file_path <- paste(base_path,"../Analyze/figures",sprintf("VlnPlot_%s_%s_exp.png",gsub("/",".",clust),cur_gene),sep="/")
		if(file.exists(file_path)){
			
			cat('\n![Violin Plot](',file_path,')\n\n')
		}
		file_path <- paste(base_path,"../Analyze/figures",sprintf("FeaturePlot_%s_%s_exp.png",gsub("/",".",clust),cur_gene),sep="/")
		if(file.exists(file_path)){
			
			cat('\n![Feature Plot](',file_path,')\n\n')
		}
	}
	
	
	grep_list <- grep(sprintf("violin_gene_.*%s.*",clust),list.files(paste(base_path,"../Analyze/figures",sep="/")),value= T)
	for (file in grep_list){
		gene <- (unlist(strsplit(file,"_"))[3])
		cat("\n\n#### ",cur_gene,"\n\n")
		cat('\n![Compare](',file_path,')\n\n')
	}
	
	
}
```



# Velocity DE scores table

This applies a differential expression test (Welch t-test with overestimated variance to be conservative) on velocity expression, to find genes in a cluster that show dynamics that is transcriptionally regulated differently compared to all other clusters (e.g. induction in that cluster and homeostasis in remaining population).

A positive high score indicates that the velocity of that gene in the cluster is high compared to that gene in other clusters.



```{r ta_vel, echo = F, warning = F}
v_table <- read.delim(paste(outdir,"Analyze","top_cluster_velocity_genes.tsv",sep="/"))
v_table <- v_table[,-1]
datatable(v_table)
```


```{r echo = F, warning = F, results = 'asis', eval = F}
Heatmap of highest and lowest scores in each cluster

file_path <- paste(base_path,"../Analyze/figures/heatmap_velocity_scores.png",sep="/")
if(file.exists(file_path)){
	cat('\n![Heatmap](',file_path,')\n\n')
}
```


# Partion-based graph abstration


```{r paga, echo = F, warning = F, results = 'asis'}
file_path <- paste(base_path,"../Analyze/figures/scvelo_PAGA.png",sep="/")
if(file.exists(file_path)){
	cat('\n![PAGA](',file_path,')\n\n')
}
```

# Pseudotime


```{r pseudo, echo = F, warning = F, results = 'asis'}
file_path <- paste(base_path,"../Analyze/figures/scvelo_pseudotime.png",sep="/")
if(file.exists(file_path)){
	cat('\n![pseudotime](',file_path,')\n\n')
}
```




# Session Info

```{r echo = F}
sessionInfo()
```

